Invariant Generation using ACDL

### 2016-08-06 invariant.tex
minor algo modifications

\input{symbols}
\input{refs}

@@

\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{decide}{Decide}
\SetKwFunction{deduce}{deduce}
\SetKwFunction{backtrack}{backtrack}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{nondet}{nondet}
\SetKwFunction{run}{run}
\SetKwFunction{learn}{learn}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwRepeat{Do}{do}{while}
%\SetKwFunction{assume}{assume}
%\SetKwFunction{isf}{isFeasible}
\SetKwData{safe}{safe}
\SetKwData{unsafe}{unsafe}
\SetKwData{sat}{sat}
\SetKwData{unsat}{unsat}
\SetKwData{unknown}{unknown}
\SetKwData{true}{true}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKw{KwNot}{not}
\begin{small}
\Input{Formula $\mathcal{F}$}
\Output{The status (\sat or \unsat or \unknown)}
%\tcc{The initial state}
%$ACDL \leftarrow \tuple{\neg(assert(c)),loopselect=nondet}$ \nllabel{algline:initPS}\;
\assign result=\deduce(F)\;
\uIf{$result == \perp$} {
  \return \unsat \;
}
\uElse
{
  \uIf{is\_complete()} {
    \return \sat \;
  }
}
\While{$true$} 
{
  \assign decision\_variable = decision\_heuristics($F$)\;
  \assign decision\_container = decision\_container $\cup$ decision\_variable\; 
  \uIf{decision\_variable == NULL}
  {
    return \unknown\; 
  }
  \uElse
  {
    \assign result=\deduce(F)\;
    \uIf{result == UNKNOWN}
    {
      \uIf{is\_complete()} {
        \return \sat \;
      }
      \uElse 
      {
        \continue\;
      }
    }
    \uElse
    {
      \Do{result == PASS} {
        \uIf{$\neg$ conflict\_analysis()} {
          return \unsat \;  
        }
        \assign result=\deduce(F)\;
      }
    }
  }
}
\end{small}
\caption{ACDCL Solver \label{Alg:acdl}}
\end{algorithm2e}

\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{decide}{Decide}
\SetKwFunction{deduce}{deduce}
\SetKwFunction{backtrack}{backtrack}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{nondet}{nondet}
\SetKwFunction{run}{run}
\SetKwFunction{learn}{learn}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwRepeat{Do}{do}{while}
%\SetKwFunction{assume}{assume}
%\SetKwFunction{isf}{isFeasible}
\SetKwData{safe}{safe}
\SetKwData{unsafe}{unsafe}
\SetKwData{unknown}{unknown}
\SetKwData{true}{true}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKw{KwNot}{not}
\begin{small}
\Input{Program $\mathcal{P}$ with properties specified with $assert(c)$}
\Output{The status (\safe or \unsafe) and a counterexample if \unsafe}
%\tcc{The initial state}
$ACDCL-P \leftarrow \tuple{\neg(assert(c)),loopselect=nondet}$ \nllabel{algline:initPS}\;
\assign result=\deduce(P)\;
\uIf{$result == \perp$} {
  \return \safe \;
}
\uElse
{
  \uIf{is\_complete()} {
    \return \unsafe \;
  }
}
\While{$true$} 
{
  \assign decision\_variable = decision\_heuristics($P$)\;
  \assign decision\_container = decision\_container $\cup$ decision\_variable\; 
  \uIf{decision\_variable == NULL}
  {
    return \unknown\; 
  }
  \uElse
  {
    \assign result=\deduce(P)\;
    \uIf{result == UNKNOWN}
    {
      \uIf{is\_complete()} {
        \return \unsafe \;
      }
      \uElse 
      {
        \continue\;
      }
    }
    \uElse
    {
      \Do{result == PASS} {
        \uIf {loop\_variable $\in$ decision\_container} {
          \assign $Inv=(\bigcap_{i=1}^{n} d_{i} \rightarrow
              \bigcap_{j=1}^{m} l_{j})$ where $d_i$ $\in$ \{non\_loop\_variable 
            $\cup$ loop\_variable\}, $l_j$ $\in$ \{loop\_variable\} \nllabel{algline:inv}\;
            \assign Inv\_formula = $Inv$ $\wedge$ $P$ $\wedge$ $Inv'$, where $Inv'$
            is the invariant after the application of transition system\;
        $inv\_result \leftarrow$ run($ACDCL$, $Inv\_formula$) \; 
        \uIf{inv\_result == UNSAT \nllabel{algline:statusIS}} {
          \learn $Inv$ \;
        }
        }
        \uIf{$\neg$ conflict\_analysis()} {
          return \safe \;  
        }
        \assign result=\deduce(P)\;
      }
    }
  }
}
\end{small}
\caption{ACDCL-P Verifier with Invariant Checking\label{Alg:verifox}}
\end{algorithm2e}

\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{decide}{Decide}
\SetKwFunction{deduce}{deduce}
\SetKwFunction{backtrack}{backtrack}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{nondet}{nondet}
\SetKwFunction{run}{run}
\SetKwFunction{learn}{learn}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwRepeat{Do}{do}{while}
%\SetKwFunction{assume}{assume}
%\SetKwFunction{isf}{isFeasible}
\SetKwData{safe}{safe}
\SetKwData{unsafe}{unsafe}
\SetKwData{true}{true}
\SetKwData{false}{false}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKw{KwNot}{not}
\begin{small}
\Input{A counterexample trace $t$ of Program $P$}
\Output{The status (\true) if $t$ is not spurious and $t$ is complete 
or (\false) if $t$ is spurious or not complete}
\uIf{loopselect $\in$ t} {
   \uIf{loopselect==false} {
      \uIf{gamma\_complete(t)} {
        return \true \;
      }
      \uElse 
      {
        return \false \;
      }
   }
   \uElse {
     return \false \;
   }
}
\end{small}
\caption{Spurious Counterexample Checking \label{Alg:spurious-check}}
\end{algorithm2e}

>>>>

\input{symbols}

@@

\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{decide}{Decide}
\SetKwFunction{deduce}{deduce}
\SetKwFunction{backtrack}{backtrack}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{nondet}{nondet}
\SetKwFunction{run}{run}
\SetKwFunction{learn}{learn}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwRepeat{Do}{do}{while}
%\SetKwFunction{assume}{assume}
%\SetKwFunction{isf}{isFeasible}
\SetKwData{safe}{safe}
\SetKwData{unsafe}{unsafe}
\SetKwData{sat}{sat}
\SetKwData{unsat}{unsat}
\SetKwData{unknown}{unknown}
\SetKwData{true}{true}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKw{KwNot}{not}
\begin{small}
\Input{Formula $\mathcal{F}$}
\Output{The status (\sat or \unsat or \unknown)}
%\tcc{The initial state}
%$ACDL \leftarrow \tuple{\neg(assert(c)),loopselect=nondet}$ \nllabel{algline:initPS}\;
result=\deduce(F)\;
\uIf{$result == \perp$} {
  \return \unsat \;
}
\uElse
{
  $t$ = get\_counterexample\_trace\_from\_P \;
  \uIf{spurious\_check(t)}
  {
    \return \sat \;
  }
}
\While{$true$} 
{
  meet\_irreducible = decision\_heuristics($F$)\;
  decision\_container = decision\_container $\cup$ meet\_irreducible\; 
  \uIf{meet\_irreducible == NULL}
  {
    return \unknown\; 
  }
  \uElse
  {
    \assign result=\deduce(F)\;
    \uIf{result == UNKNOWN}
    {
      $t$ = get\_counterexample\_trace\_from\_P \;
      \uIf{spurious\_check(t)}
      {
        \return \sat \;
      }
      \uElse 
      {
        \continue\;
      }
    }
    \uElse
    {
      \Do{result == PASS} {
        \uIf{$\neg$ conflict\_analysis()} {
          return \unsat \;  
        }
        \assign result=\deduce(F)\;
      }
    }
  }
}
\end{small}
\caption{ACDCL Solver \label{Alg:acdl}}
\end{algorithm2e}

\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{decide}{Decide}
\SetKwFunction{deduce}{deduce}
\SetKwFunction{backtrack}{backtrack}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{nondet}{nondet}
\SetKwFunction{run}{run}
\SetKwFunction{learn}{learn}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwRepeat{Do}{do}{while}
%\SetKwFunction{assume}{assume}
%\SetKwFunction{isf}{isFeasible}
\SetKwData{safe}{safe}
\SetKwData{unsafe}{unsafe}
\SetKwData{unknown}{unknown}
\SetKwData{true}{true}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKw{KwNot}{not}
\begin{small}
\Input{Program $\mathcal{P}$ with properties specified with $assert(c)$}
\Output{The status (\safe or \unsafe) and a counterexample if \unsafe}
%\tcc{The initial state}
$ACDCL-P \leftarrow \tuple{\neg(assert(c)),loopselect=nondet}$ \nllabel{algline:initPS}\;
result=\deduce(P)\;
\uIf{$result == \perp$} {
  \return \safe \;
}
\uElse
{
  $t$ = get\_counterexample\_trace\_from\_P \;
  \uIf{spurious\_check(t)} {
    \return \unsafe \;
  }
}
\While{$true$} 
{
   meet\_irreducible = decision\_heuristics($P$)\;
   decision\_container = decision\_container $\cup$ meet\_irreducible \; 
  \uIf{meet\_irreducible == NULL}
  {
    return \unknown\; 
  }
  \uElse
  {
    result=\deduce(P)\;
    \uIf{result == UNKNOWN}
    {
      $t$ = get\_counterexample\_trace\_from\_P \;
      \uIf{spurious\_check(t)} {
        \return \unsafe \;
      }
      \uElse 
      {
        \continue\;
      }
    }
    \uElse
    {
      \Do{result == PASS} {
        \uIf {loop\_variable $\in$ decision\_container} {
              $Inv=(\bigcap_{i=1}^{n} d_{i} \rightarrow
              \bigcap_{j=1}^{m} l_{j})$ where $d_i$ $\in$ \{non\_loop\_variable 
            $\cup$ loop\_variable\}, $l_j$ $\in$ \{loop\_variable\} \nllabel{algline:inv}\;
             Inv\_formula = $Inv$ $\wedge$ $P$ $\wedge$ $\neg{Inv'}$, where $Inv'$
            is the invariant after the application of transition system\;
        $inv\_result \leftarrow$ run($ACDCL$, $Inv\_formula$) \; 
        \uIf{inv\_result == UNSAT \nllabel{algline:statusIS}} {
          \learn $Inv$ \;
        }
        }
        \uIf{$\neg$ conflict\_analysis()} {
          return \safe \;  
        }
        result=\deduce(P)\;
      }
    }
  }
}
\end{small}
\caption{ACDCL-P Verifier with Invariant Checking\label{Alg:verifox}}
\end{algorithm2e}

\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{decide}{Decide}
\SetKwFunction{deduce}{deduce}
\SetKwFunction{backtrack}{backtrack}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{nondet}{nondet}
\SetKwFunction{run}{run}
\SetKwFunction{learn}{learn}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwRepeat{Do}{do}{while}
%\SetKwFunction{assume}{assume}
%\SetKwFunction{isf}{isFeasible}
\SetKwData{safe}{safe}
\SetKwData{unsafe}{unsafe}
\SetKwData{true}{true}
\SetKwData{false}{false}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKw{KwNot}{not}
\begin{small}
\Input{A counterexample trace $t$ of Program $P$}
\Output{The status (\true) if $t$ is not spurious and $t$ is complete 
or (\false) if $t$ is spurious or not complete}
\uIf{loopselect $\in$ t} {
   \uIf{loopselect==false} {
      \uIf{gamma\_complete(t)} {
        return \true \;
      }
      \uElse 
      {
        return \false \;
      }
   }
   \uElse {
     return \false \;
   }
}
\end{small}
\caption{Spurious Counterexample Check \label{Alg:spurious-check}}
\end{algorithm2e}
